---
title: "lsr2"
author: "Danielle Navarro"
date: "3 March 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lsr2)
```

Rethinking the `lsr` package that accompanies [Learning Statistics with R](https://learningstatisticswithr.com). At the moment this is purely experimental, and is as much an exercise in teaching myself package development as anything else. It's an absurdity that I've never learned `roxygen2` until now!

Looking back, my goal in the package was not to introduce any new functionality to R, but rather to provide wrappers and simplifications that novice users (e.g., psychology undergraduate students who might be encountering R, statistics and programming for the first time ever) might find handy.

Currently the only function in the `lsr2` package is `workspace()`, which lists the contents of the calling environment in a fashion that is more verbose than `objects()` but less elaborate than `ls.str()`

```{r}
# some variables for the workspace
seeker <- "hello"
lover <- 10
keeper <- list(seeker, lover)

# now print a summary
workspace()
```

It wouldn't be difficult to add a print method for this so that the results look more similar to the simple display in the original package:

```{r}
lsr::who()
```
