---
title: "lsr2"
author: "Danielle Navarro"
date: "25 April 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lsr2)
```

[![Travis build status](https://travis-ci.org/djnavarro/lsr2.svg?branch=master)](https://travis-ci.org/djnavarro/lsr2)  [![Codecov test coverage](https://codecov.io/gh/djnavarro/lsr2/branch/master/graph/badge.svg)](https://codecov.io/gh/djnavarro/lsr2?branch=master)

Rethinking the `lsr` package that accompanies [Learning Statistics with R](https://learningstatisticswithr.com). In the original book, the goal of the package was to provide a few convenient wrapper functions and simplifications that novice users might find handy. A typical reader of the book might be psychology undergraduate students who encountering R, statistics and programming for the first time, and I found the simplifications useful in some cases.

The `lsr2` package (working title!!) is intended to accompany the next version of *Learning Statistics with R*, in which the goal is to teach a tidyverse-focused data analysis pipeline. Currently the only function in `lsr2` is `workspace()`, which lists the contents of the calling environment in a fashion that is more verbose than `objects()` but less elaborate than `ls.str()`

```{r}
# some variables for the workspace
seeker <- "hello"
lover <- 10
keeper <- list(seeker, lover)

# now print a summary
workspace()
```

It wouldn't be difficult to add a print method for this so that the results look more similar to the simple display in the original package, but I am not yet sure if this is worthwhile.

```{r}
lsr::who()
```
